\documentclass{article}

\usepackage{contour}
\usepackage[margin=.7in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{ulem}
\usepackage{xcolor}
\usepackage{fontawesome}

\renewcommand{\ULdepth}{1.8pt}
\contourlength{0.8pt}

% -------------------- Commands --------------------

% Produces the header for the resume.
% @param 1: header line
% @param 2: subheader line
\newcommand{\header}[2]{
  \begin{center}
    {\LARGE \textbf{#1}} \\
    \vspace*{4px}
    {#2} \\
  \end{center}
}

% Produces a horizontal rule.
\newcommand{\hr}{
  \noindent \makebox[\linewidth]{
    \rule{\textwidth}{1pt}
  } 
}

% Produces underlined text.
% h/t https://alexwlchan.net/2017/10/latex-underlines/
% @param 1: text
\newcommand{\myuline}[1]{%
  \color{black!80}{\uline{\phantom{#1}}}%
  \llap{\contour{white}{#1}}%
}

% Produces a section header.
% @param 1: section header text
\renewcommand{\section}[1]{
  \vspace*{5px}
  \noindent {\Large \textbf{#1}} \\
  \vspace*{-24px} \\
  \hr
  \vspace*{-10px}
}

% Produces a section subheader.
% @param 1: section subheader text
\renewcommand{\subsection}[1]{
  \noindent {\large \textbf{#1}} \\
}

% Produces a section subheader detail.
% @param 1: section subheader detail text
\newcommand{\subsectiondetail}[2]{
  \vspace*{-12px} \\
  \noindent {\myuline{#1} \hfill {#2}} \\
}

% Produces indented text.
% @param 1: text
\newcommand{\listitem}[1]{
  $\bullet$ {#1} \\
}

% Produces the footer for the resume.
% @param 1: footer line 1
\newcommand{\footer}[1]{
  \begin{center}
    {#1}
  \end{center}
}

% Produces a twiddle character.
\newcommand{\twiddle}{\raise.2ex\hbox{$\scriptstyle\sim$}}

% Produces a GitHub icon.
\newcommand{\github}{\faGithubAlt \space}

% Produces a LinkedIn icon.
\newcommand{\linkedin}{\faLinkedinSquare \space}

% Produces a Globe icon.
\newcommand{\globe}{\faGlobe \space}

% -------------------- Document --------------------

\setlength{\parindent}{13pt}
\linespread{1.3}
\pagestyle{empty}
\begin{document}

% --------------------- Header ---------------------
\header
    {Joe Brunner}
    {\href{https://github.com/brunner}{\github github.com/brunner} $\cdot$
    \href{https://linkedin.com/in/brunnerj}{\linkedin linkedin.com/in/brunnerj}}

% ------------------- Employment -------------------
\section
    {Employment}

\subsection
    {Block}
\subsectiondetail
    {Staff Software Engineer, Orders Platform and Customer Operations}
    {07/2021 – present}
\listitem
    {Owned critical Orders APIs (Kotlin, Go) and Pricing crossplatform (Swift,
        Kotlin Multiplatform) infrastructure.}
\listitem
    {Steered modernization of Customer Ops components (Ruby, React, GraphQL)
        and data analysis (Snowflake, Looker).}
\listitem
    {Led improvements to operational processes and system health monitoring to
        ensure high availability and performance.}
\listitem
    {Fostered engaging and collaborative team environments where other
        engineers successfully grow their careers.}
\subsectiondetail
    {Senior Software Engineer, Subscriptions APIs and Orders Platform}
    {03/2019 – 07/2021}
\listitem
    {Coordinated end-to-end launches of core Orders features such as customer
        discounts and itemized service charges.}
\listitem
    {Scaled Orders discounting and calculating APIs from their inception to
        supporting millions of daily requests.}
\listitem
    {Built and released public Square Developer APIs enabling businesses to
        sell product subscriptions to customers.}

\subsection
    {Google}
\subsectiondetail
    {Software Engineer, Core Search Features and Search Platforms}
    {06/2014 – 03/2019}
\listitem
    {Maintained the Search frontend web server (Java, Python, XML) delivering
        results to billions of users worldwide.}
\listitem
    {Implemented the UI layer of many core features such as organic Search
        results and real-time (e.g. Twitter) results.}
\listitem
    {Pioneered architecture to drive rapid adoption of long-tail Search
        features on emerging clients and low-end networks.}

\subsection
    {FactSet Research Systems}
\subsectiondetail
    {Software Engineer Intern, Idea Screening}
    {05/2013 – 08/2013}
\listitem
    {Created a profiling tool to trace calls and identify bottlenecks across
        financial reporting APIs and frontends.}

% ------------------- Education --------------------
\section
    {Education}

\subsection
    {University of Rochester}
\subsectiondetail
    {Bachelor of Science, Computer Science; Bachelor of Arts, Mathematics}
    {09/2010 – 05/2014}
\listitem
    {Cumulative GPA of 3.61/4.0, earning degrees in Computer Science (core GPA
        of 3.68) and Mathematics (3.53).}
\listitem
    {Worked on IT student staff for four years, resolving account and
        network issues for university faculty and students.}
\listitem
    {Managed hiring, scheduling, and training for over two years as IT student
        lead to \twiddle20 other student employees.}

% ------------------- Projects --------------------
\section
    {Projects}

\subsection
    {Filefairy}
\subsectiondetail
    {Creator, \href{https://github.com/brunner/filefairy}{\github github.com/brunner/filefairy} and \href{https://brunnerj.com/fairylab}{\globe brunnerj.com/fairylab}}
    {10/2016 – 05/2019}
\listitem
    {Developed an extensible application to enhance game data generated from an
        online Out of the Park Baseball league.}
\listitem
    {Surfaced a dynamically generated web UI illustrating the current game
        state for increased stakeholder accessibility.}
\listitem
    {Prioritized resiliency to data provider changes through careful module
        isolation and on-demand app reloading.}

% --------------------- Footer ---------------------
\footer
    {Last updated April 2025}

\end{document}
